### 2013-03-28 doc/sosp13/evaluation.tex
profile

\begin{figure}[ht]
    \begin{center}
      \begin{tabular}{c|c c c c}
        Benchmark     & Comm & User & Idle & Sched \\ \hline
        GUPS          & 6.60  & 42.94   & 47.74 & 2.80 \\
        BFS           & 54.84 & 30.90   & 10.94 & 3.43 \\ 
        Intsort       & 34.28 & 42.00   & 21.31 & 2.47 \\ 
        UTS           & 40.57 & 56.52   &  1.21 & 1.73 \\
        Pagerank      & 76.79 & 20.71   &  0.06 & 2.50 \\
      \end{tabular}
    \end{center}
    \caption{\Grappa\ execution time profile, in percent.}
%bar chart, one set of bars per benchmark, one bar per system. runtime normalized to grappa.
    \label{fig:grappa-profile}
\end{figure}

\TODO{PAGERANK:
    Without parallelizing the dot product, \Grappa cannot achieve
high utilization of workers proportional to the size of the data set.
Also mention that the cost of this is contention at the target
elements of vector.  The other parts of pagerank are super fast
(table?)
}

>>>>

\begin{figure}[ht]
    \begin{center}
      \begin{tabular}{c|c c c c}
        Benchmark     & Comm & User & Idle & Sched \\ \hline
        GUPS          & 62.9  & 18.9    & 15.4 & 2.80 \\ 
        BFS           & 54.84 & 30.90   & 10.94 & 3.43 \\ 
        Intsort       & 34.28 & 42.00   & 21.31 & 2.47 \\ 
        UTS           & 40.57 & 56.52   &  1.21 & 1.73 \\
        Pagerank      & 76.79 & 20.71   &  0.06 & 2.50 \\
      \end{tabular}
    \end{center}
    \caption{\Grappa\ execution time profile, in percent.}
%bar chart, one set of bars per benchmark, one bar per system. runtime normalized to grappa.
    \label{fig:grappa-profile}
\end{figure}

Figure \ref{fig:grappa-profile} shows the breakdown of execution
time. Since \Grappa is focused on frequent communication, it is not
surprising that many of our benchmarks spend more than half of their
time doing communication. User time is primarily focused on generating
more requests; idle time occurs when we run out of parallel work or
out of workers to execute that work. Scheduler time includes both
context switch time and deciding what task to run next. Our efficient
context switching allows us to keep this to a few percent of execution
time even with thousands of threads per core.
